API design for machine learning software: experiences from the scikit-learn project

### 2013-09-11 paper.tex
rewrite the introduction
In the CiSE format, it's below or next to the abstract, which it was
repeating. Also upped the sales pitch.

The \sklearn project \citep{pedregosa2011} provides an open source machine learning
library for the Python programming language. The ambition of the project is to
provide efficient and well-established machine learning tools within a
programming environment that is accessible to non-machine learning experts and
reusable in various scientific areas. The project is not a novel domain-specific
language, but a library that provides machine learning idioms to a
general-purpose high-level language. It includes classical learning algorithms,
model evaluation and selection tools, as well as preprocessing procedures.
The library is distributed under the simplified BSD license,
encouraging its use in both academia and industry.

\sklearn is a library, i.e.\ a collection of classes
and functions that users import into Python programs.
No command-line interface, let alone a graphical user interface,
is offered for non-programmer users. Instead,
interactive use is made possible by the Python interactive interpreter, and its
enhanced replacement IPython \citep{perez2007ipython}, which offers a
\textsc{matlab}-like working environment especially suited for scientific use.

The library has been designed to tie in with the set of numeric
and scientific packages centered around the NumPy and SciPy libraries. NumPy
\citep{vanderwalt2011} augments Python with a contiguous numeric array datatype
and fast array computing primitives,
while SciPy \citep{varoquaux2013scipy} extends it
further with common numerical operations, either by implementing
these in Python/NumPy or by wrapping existing C/C{}\verb!++!/Fortran
implementations. Building upon this stack, a series of libraries called
\textit{scikits} were created, to complement SciPy with
domain-specific toolkits. Currently, the two most popular and feature-complete
ones are by far \sklearn and
\textit{scikit-image},\footnote{\url{http://scikit-image.org}}
which does image processing.

Since 2007, \sklearn has been developed by an international team of more than a dozen
core developers, mostly researchers from various fields (e.g.,
computer science, neuroscience, astrophysics). The project also benefits
from many occasional contributors proposing small bugfixes or
improvements. Development proceeds on GitHub\footnote{\url{https://github.com/scikit-learn}},
a platform which greatly facilitates this kind of
collaboration. Because of the large number of developers, emphasis is
put on keeping the project maintainable. In particular, code must follow
specific quality guidelines, such as style consistency and unit-test coverage.
Documentation and examples are required for all features,
and major changes must pass code review by at least two
developers not involved in the implementation of the proposed change.

>>>>

Many science and engineering disciplines are trying to make sense
of ever-increasing volumes of information.
Machine learning (ML) promises to alleviate this problem
by automating the process of finding patterns in the rising sea of data,
but ML tools can be hard to use
and in particular, hard to combine
when multiple algorithms are needed for a task.

The \sklearn project provides a comprehensive suite of machine learning tools,
packaged as a library for the Python programming language.
It extends this general-purpose language with machine learning operations:
learning algorithms, preprocessing tools, model selection procedures
and a composition mechanism to produce complex ML workflows.
The ambition of the project is to provide efficient implementations
of well-established ML algorithms within a
programming environment that is accessible to non-experts and
reusable in various scientific areas.
The library is distributed under the simplified BSD license
to encourage its use in both academia and industry.

\sklearn is designed to tie in with the set of numeric
and scientific packages centered around the NumPy and SciPy libraries. NumPy
\citep{vanderwalt2011} augments Python with a contiguous numeric array datatype
and fast array computing primitives,
while SciPy \citep{varoquaux2013scipy} extends it
further with common numerical operations, either by implementing
these in Python/NumPy or by wrapping existing C/C{}\verb!++!/Fortran code.
The name ``scikit'' derives from (domain-specific) ``SciPy toolkit''
and is shared with \textit{scikit-image}.\footnote{\url{http://scikit-image.org}}
IPython \citep{perez2007ipython} and Matplotlib \citep{hunter2007matplotlib}
complement SciPy to provide a \textsc{matlab}-esque working environment
suited for scientific use.

Since 2007, \sklearn has been developed by more than a dozen
core developers, mostly researchers in various fields
(a.o.\ computer science, neuroscience, astrophysics). It also benefits
from occasional contributors proposing small bugfixes or
improvements. Development proceeds on GitHub\footnote{\url{https://github.com/scikit-learn}},
a platform which greatly facilitates this kind of
collaboration. Because of the large number of developers, emphasis is
put on keeping the project maintainable. In particular, code must follow
specific quality guidelines, such as style consistency and unit-test coverage.
Documentation and examples are required for all features,
and major changes must pass code review by at least two
developers not involved in the implementation of the proposed change.
